A user--friendly tool to evaluate the effectiveness of no--take marine reserves

### 2017-11-06 Manuscript.Rmd
updated the repository with the submitted version

---
title: A user--friendly tool to evaluate the effectiveness of no--take marine reserves
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
output:
  word_document:
    fig_caption: yes
fontsize: 12pt
bibliography:
- exported-references.bib
- packages.bib
csl: plos.csl
---

@@

Marine reserves are implemented to achieve a variety of objectives, but are seldom rigorously evaluated to determine whether those objectives are met. In the rare cases when evaluations do take place, they typically focus on ecological indicators and ignore other relevant objectives such as socioeconomics and governance. And regardless of the objectives, the diversity of locations, monitoring protocols, and analysis approaches hinder the ability to compare results across case studies. Moreover, analysis and evaluation of reserves is generally conducted by outside researchers, not the reserve managers or users, plausibly thereby hindering effective local management and rapid response to change. We present a framework and tool, called “MAREA”,to overcome these challenges. Its purpose is to evaluate the extent to which any given reserve has achieved its stated objectives.  MAREA provides specific guidance on data collection and formatting, and then conducts rigorous causal inference analysis based on data input by the user, providing real--time outputs about the effectiveness of the reserve. MAREA’s ease of use, standardization of state--of--the--art inference methods, and ability to analyze marine reserve effectiveness across ecological, socioeconomic, and governance objectives could dramatically further our understanding and support of effective marine reserve management.

@@

$$I_{i,t,z}=\beta_0 + \sum_{t = 2}^T\gamma_{t}Y_t + \beta_1Z_{i,z} + \beta_2P_{i,t}\times Z_{i,z} + \beta_3T_{i,t,z} + \beta_4V_{i,t,z} + \beta_5D_{i,t,z} + \epsilon_{i,t,z}$$

@@

$$I_t = RI\times \frac{CPI_t}{CPI_T}$$

@@

$$I_{t}=\beta_0 + \beta_1P_{t} + \epsilon_{t}$$

@@

# Funding

- CF and JCVD received support from the Latin American Fisheries Fellowship Program.
- JCVD received support from the Consejo Nacional de Ciencia y Tecnología (CONACyT).
- GM received financial support from Waitt Foundation.
- Biological data for Isla Natividad were collected with the support of the Walton Family Foundation, the NSF-CNH program (grant DEB-1212124), Marisla Foundation, Sandler Family Supporting Foundation, and Packard Foundation.
- AS received support from The Nature Conservancy and World Wildlife Fund--Carlos Slim Foundation Alliance

@@

# Figures

![Workflow to evaluate the effectiveness of marine reserves.](./Figures/flowchart.gif){ width="50%"}

```{r, fig.cap = "Legend used to interpret the scorecard produced by MAREA. Colors indicate direction of change (red = negative; green = positive), and color intensity is given by the statistical significance"}
fig2
```

```{r, fig.cap = "General location of Isla Natividad (left) and map of the island (right). The marine reserve polygon is indicated in red, and the approximate location of control sites is indicated by blue squares (B = Babencho, D = La Dulce)."}
tmap_arrange(pen_map, study_area, outer.margins = 0.005, ncol = 2)
```

![Scorecard produced by MAREA for the "La Plana / Las Cuevas" marine reserve in Isla Natividad, Mexico.](./Figures/scorecard.png){ width=80% }

```{r, fig.height = 6, fig.width = 6, fig.cap = "Plots for values of each biological indicator (y-axis) through time (x-axis). Red and blue correspond to the reserve and control sites, respectively. Black lines indicate yearly mean values, and ribbons indicate +/- 1 standard error. Dots are horizontally jittered to aid visualization. This figure contains information for fish shannon diversity index (a), fish species richness (b), fish density (c), fish trophic level (d), fish biomass (e), invertebrate shannon diversity index (f), invertebrate species richness (g), invertebrate density (h), lobster density (i), urchin density (j), snail density (k), and sea cucumber density (l)."}
gridExtra::grid.arrange(shannon_fish_plot, richness_fish_plot, density_fish_plot, trophic_fish_plot, biomass_fish_plot, shannon_invert_plot, richness_invert_plot, density_invert_plot, lobster_density_invert_plot, urchin_density_invert_plot, snail_density_invert_plot, cucumber_density_invert_plot, ncol = 3)
```

```{r, fig.height = 6, fig.width = 6, fig.width = 6, fig.cap = "Plots for values of each socioeconomic indicator (y-axis) through time (x-axis). Red and blue correspond to before and after the implementation of the reserve, respectively. This figure contains information for total landings (a), total income (b), lobster landings (c), urchin landings (d), snail landings (e), sea cucumber landings (f), lobster income (g), urchin income (h), snail income (i), and sea cucumber income (j)."}
gridExtra::grid.arrange(landings_plot, income_plot, landings_lobster_plot, landings_urchin_plot, landings_snail_plot, landings_cucumber_plot, income_lobster_plot, income_urchin_plot, income_snail_plot, income_cucumber_plot, ncol = 3)
```

>>>>

---
title: A user--friendly tool to evaluate the effectiveness of no--take marine reserves
subtitle: Marine reserve evaluation
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
fontsize: 12pt
bibliography:
- exported-references.bib
- packages.bib
csl: plos.csl
---
<script type="text/x-mathjax-config">
MathJax.Hub.Config({
  TeX: { 
      equationNumbers: { 
            autoNumber: "all",
            formatNumber: function (n) {return '9.'+n}
      } 
  }
});
</script>

@@

Marine reserves are implemented to achieve a variety of objectives, but are seldom rigorously evaluated to determine whether those objectives are met. In the rare cases when evaluations do take place, they typically focus on ecological indicators and ignore other relevant objectives such as socioeconomics and governance. And regardless of the objectives, the diversity of locations, monitoring protocols, and analysis approaches hinder the ability to compare results across case studies. Moreover, analysis and evaluation of reserves is generally conducted by outside researchers, not the reserve managers or users, plausibly thereby hindering effective local management and rapid response to change. We present a framework and tool, called “MAREA”, to overcome these challenges. Its purpose is to evaluate the extent to which any given reserve has achieved its stated objectives.  MAREA provides specific guidance on data collection and formatting, and then conducts rigorous causal inference analysis based on data input by the user, providing real--time outputs about the effectiveness of the reserve. MAREA’s ease of use, standardization of state--of--the--art inference methods, and ability to analyze marine reserve effectiveness across ecological, socioeconomic, and governance objectives could dramatically further our understanding and support of effective marine reserve management.

@@

\begin{equation}I_{i,t,z}=\beta_0 + \sum_{t = 2}^T\gamma_{t}Y_t + \beta_1Z_{i,z} + \beta_2P_{i,t}\times Z_{i,z} + \beta_3T_{i,t,z} + \beta_4V_{i,t,z} + \beta_5D_{i,t,z} + \epsilon_{i,t,z}\end{equation}

@@

\begin{equation}I_t = RI\times \frac{CPI_t}{CPI_T}\end{equation}

@@

\begin{equation}I_{t}=\beta_0 + \beta_1P_{t} + \epsilon_{t}\end{equation}

@@

@@
